Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-06-01 paper/paper.tex
Lots of authors

\title{Observations from Parallelising Three Maximum Common Subgraph Algorithms}

\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]} \and Patrick Prosser \and James Trimble\samethanks[1]}

\institute{University of Glasgow, Glasgow, Scotland,\\
\email{c.mccreesh.1@research.gla.ac.uk}}

@@

>>>>

\title{Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms}

\author{Ruth Hoffmann \inst{1} \and Ciaran McCreesh\thanks{This work was supported by the
Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1, EP/M508056/1, and EP/M508056/1]}
\inst{2} \and Patrick Prosser \inst{2} \and Samba Ndojh Ndiaye\thanks{This work
was supported by the ANR project SoLStiCe (ANR-13-BS02-0002-01)} \inst{3}
\and Craig Reilly \samethanks[1] \inst{2}
\and Christine Solnon\samethanks[2]\inst{4} \and James Trimble\samethanks[1] \inst{2}}

\institute{
    University of St Andrews, St Andrews, Scotland
    \and University of Glasgow, Glasgow, Scotland
    \and Universit\'e Lyon 1, LIRIS, UMR5205, F-69621, France
    \and INSA-Lyon, LIRIS, UMR5205, F-69621, France \\
    \email{c.mccreesh.1@research.gla.ac.uk}}

@@

\section{Sequential Algorithms}

\subsection{A Basic Constraint Model}

\subsection{Ensuring Connectedness}

\subsection{The Splitting Algorithm}

\subsection{The Clique Encoding}

\subsection{The $k$-less Subgraph Isomorphism Algorithm}

\section{Parallel Search}

\section{Experiments}

\section{Conclusion}
